Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-08 paper.tex

        Workflows, also known as pipelines, describe the flow of data from 
        activity to another. They are typically represented by a 
        Directed Acyclic Graph (DAG) \tristan{Not necessarily a DAG, see Nipype for instance, it has loops.
        I don't think you want to enter in a taxonomy of languages though, just say 'graph'}. Workflow activites, also referred to as 
        workflows stages, encapsulate a tool \tristan{Mention 'interface' here as an intro to sub-sec 2}. Tools may either take the form of 
        a command-line tool or a custom script \tristan{A script is a command-line tool. I think tools may also be web services (Taverna) or just 
        software libraries (Dask)}. The engines determine which
        workflow activity can be staged by determining if the stage dependencies
        have been satisfied.

        In order for a workflow engine to be successful, it must be simple to 
        compose workflows using that framework. New researchers should be able 
        to acquire the skills to compose worfklows in that framework without
        investing a significant amount of time in understanding it. Reuse of
        existing tools is also common occurrence in neuroinformatics and 
        workflow engines need to accomodate this by undertaking a modular 
        approach and being easily extensible. With the sharing of data also 
        comes the sharing of workflows. For labs to share their workflows with
        the community at large, these workflows must be easily understood by the
        community. \tristan{Perhaps mention that this also relates to the sharing
        of reproducible results}.

        In this Chapter, we will compare and contrast the workflow composition 
        of seven neuroimaging frameworks (SPM, LONI, Nipype, PSOM, FastR, AA and
        Pydpiper), seven scientific workflow engines stemming from other fields
        (Taverna, Pegasus, Make, OpenMOLE, Nextflow, Galaxy, Toil), and three
        BigData frameworks (MapReduce, Spark, Dask). We will use three axes to
        evaluate workflow composition. Section~\ref{lang} will compare the 
        framework on the basis of programming language used, whereas 
        Section~\ref{mod} will look at how easy it is to integrate existing 
        tools into the workflows. Section~\ref{sharing} will evaluate the ease
        at which their corresponding workflows can be shared.

        \section{Workflow language}\label{lang}
            The choice of workflow language (e.g. GUI, scripting language,
            programming language) greatly
            affects how easily it will get picked up by the community. Complex
            languages may mean greater efficiency of the engines
            , but also result in extensive time spent on learning and developing
            the pipelines. Moreover, some researchers may not be well-versed in
            programming and may require very easy-to-use engines.

            To address this issue, some workflow engines have taken the route
            of employing a graphical user interface (GUI). This makes workflow 
            composition accessible to all researchers, including those with
            little to no programming background. The caveat to employing a 
            workflow engine with a GUI interface for workflow composition is
            that users are greatly limited by the tasks they can perform. 
            Workflow engines that employ a worfklow composition GUI include
            SPM, Taverna, OpenMOLE, LONI and Galaxy. \note{double-check that 
            none have a programming API.Loni does..i think SPM does too}
            \tristan{My conclusion on GUIs is that they are suitable only
            for very simple pipelines. Perhaps the intro could give an idea
            of the types of pipelines encountered, showing a simple one and
            a more complex one. No way fmriprep is described in a GUI.}

            As more experienced programmers may feel limited by a GUI, workflow
            engines have decided to provide users with the ability to describe
            their workflows in more flexible formats. Even those with GUIs for 
            workflow composition, such as LONI and OpenMOLE, allow more 
            experienced users to script their workflow. Six different 
            programming
            languages are used for describing scientific workflows: 1) Python, 
            2) MATLAB and Octave \tristan{I think the official name is GNU/Octave}, 3) Shell \tristan{scripting languages}, 4) XML, 6) Common Workflow Language 
            (CWL) and 6) Domain Specific Language (DSL). \tristan{I don't see why CWL and XML don't qualify as DSL} Workflows engines that 
            employ usage of Python include: Nipype, FastR, Pydpiper, Pegasus
            and Toil \tristan{Dask? Spark?}.
            Python is an excellent choice as a programming language for 
            scientific workflows, particularly neuroinformatics, due to its 
            widespread use within the community. Other advantages of 
            programming in Python including a wide array of available libraries,
            including neuroimaging-specific ones such as Nilearn and Nibabel \tristan{mention scipy, sci-kit learn, etc}
            \note{cite}, and an lower learning curve compared to other 
            programming languages. Additionally, Python is platform independent
            meaning it can be installed on any system. In terms of BigData 
            frameworks that employ Python, Dask is exclusively written in Python
            , whereas Hadoop MapReduce and Spark both have interfaces to Python
            while being written in Java and Scala, respectively.

            Another widely-used high-level programming language in the 
            neuroinformatics community is MATLAB/Octave. Workflow engines which
            use this language include: PSOM, SPM, and Automatic analysis. A 
            downfall to imposing MATLAB as programming language is that the 
            it is proprietary, thus imposing a fee on 
            anyone wishes to program in that language \tristan{You should also mention the
            advantage of Matlab: easy to learn, integrated ecosystem, 
            performance, see 
            \url{https://www.mathworks.com/products/matlab/matlab-vs-python.html}}. 
            To offset this, PSOM ensure compatibility with the GNU 
            Octave programming language, thus 
            removing the requirement to purchase software for workflow 
            composition. Similarly to Python, MATLAB and Octave are 
            high-level platform-independent languages. MATLAB, in particular,
            also provides a wide array of libraries, however, the software must
            be purchased in order to access them.

            \tristan{This paragraph should start with ``Shell scripting ...". The structuration of this section by language
            is great, but the writing of this paragram doesn't put it forward.}Scientific workflows are typically composed in UNIX-based 
            environments. These environments typically have Make installed by
            default eliminating the need for users to install it manually.
            Furthermore, all users who use Linux environments will typically 
            need to write some form of Shell script. This is the basis to use 
            workflow engines, such as Make, as scientific workflow engines. 
            As Make is exclusive to UNIX environments, it is not 
            platform-independent. However, Make has the flexibility of being
            easily extensible and can interface directly with any command-line
            tool. Shell scripting, nevertheless, is generally not as intuitive
            as programming languages like Python and MATLAB.

            Composing workflows in XML is another option provided by some 
            workflow engines such as Pegasus and LONI. However, the use of a 
            markup language removes some of the flexibility. \tristan{Before you explain the downside, 
            you should say what are the advantages: mainly language-independent parsers and validation.} Users wanting to 
            include 
            custom scripts as workflow activities must do so by creating a 
            command-line interface for their custom script. Pegasus, however,
            does provide many interfaces to describe the pipeline in including
            Java, Python and Perl.

            Another alternative is to compose workflows using Common Workflow
            Language (CWL). This can be seen in workflow engines like Toil. 
            CWL is not a programming language, but a specification for workflows
            \tristan{It is a YAML-based DSL for workflows. Just like Pegasus' DAX is an XML-based DSL}. Files can either be written in JSON or YAML formats. CWL is 
            based on workflow engines like Make \tristan{? I don't think CWL relies on make, does it?}, but differs in that tasks
            are isolated and inputs and outputs must be explicit \tristan{inputs and outputs are somewhat explicit in a Makefile}. Similarly to 
            make, CWL is only available on UNIX platforms \tristan{strange, the CWL interpreter is in Python so I'd expect it to run anywhere}. \note{cite cwl 
            website}

            Domain Specific Languages (DSL) are also used to compose workflows.
            DSLs are programming languages that have been adapted to specific
            domains. Workflow engine examples include OpenMOLE, which was 
            derived from Scala, and Netflow \tristan{Nextflow?}, which is derived from the Apache 
            Groovy programming language. While both are written on top of the 
            Java platform, Nextflow is only compatible with UNIX-based \tristan{How about using Linux everywhere instead of UNIX-based?} 
            environments. These programming languages are not otherwise commonly
            used in neuroimaging, meaning that users must learn specific 
            languages that would not otherwise be used in their field.

@@

            MapReduce, Spark and Dask all provide interfaces to Python, making 
            them good candidates for neuroimaging workflow engines. In addition
            Spark also interfaces with R, another programming language commonly
            used in neuroimaging.

            \subsection{Data structures}
                \subsubsection{Scientific workflows}
                \subsubsection{Big Data: MapReduce}

            \tristan{So this is now about data structures, not just language.
            This is really excellent, but this should perhaps go into a 
            specific sub-section. I think you could mention that 
            scientific workflow engines traditionally rely on files 
            only, and simple types, but that big data engines have 
            invested a lot in data structures, starting from key-value 
            pair representations in MR to RDD and Dask arrays. Spark is 
            actually built around RDDs, this is salient-enough to be 
            discussed a bit more. It actually makes a lot of sense that 
            data-focused engines are built around data structures 
            instead of control constructs. The ACM Com Spark paper makes it clear
            that unifying data structures is key to performance and interoperability, 
            because it allows data to remain in-memory instead of having to go back
            and forth to different environments. I would only mention linealg 
            in the description of Dask arrays. So, how about a 
            sub-section 'data structures' with 4 paragraphs: (1) 
            scientific and neuroimaging engines, (2) Big-Data, MR, (3) 
            Spark's RDDs and DataFrames, (4) Dask arrays, mentioning 
            linealg. } Additionally, BigData frameworks are better 
            suited for the 
            processing of large images. Scientific workflows are generally 
            file-based with neuroimaging frameworks only providing parallelism
            on the file front. Sparks main abstraction, the Resilient 
            Distributed Dataset (RDD), permits users to process large datasets.
            A library based on the RDD, \textit{linealg}, allows users to create
            vectors and matrices and use common Python libraries, such as 
            Numpy and Scikit-learn to manipulate the data. Dask similarly 
            provides the Dask bag for file manipulation, and the Dask array for
            the manipulation of large matrices. Dask provides its own API for
            the processing of large matrices that is based on Numpy. 
            Both frameworks also provide data structures to manipulate tabular
            data: the Spark Dataframe and the Dask Dataframe. Unlike Spark, the
            Dask Dataframe is based off of the Pandas Dataframe API.

        \section{Tool interfaces}\label{mod}
            \tristan{Since this section is about interfaces, I would
            rather call it ``Interfaces" or ``Tool interfaces".}
            Often times, users will want to integrate existing tools, in 
            addition to custom scripts, into their workflows. As workflow 
            engines, with the exception of Make, are typically not written in 
            Shell, it is necessary to create interfaces to these tools. These
            interfaces may range from simple calls to the command-line, to more 
            complex ones that track inputs, outputs and other parameters; ensure
            that all parameters are specified in the correct order and that the
            parameter and file types are all correct; capture all of the 
            standard input/output; and create folders to encapsulate task inputs
            and outputs. Workflow engines typically rely on more complex types 
            of interfaces in order to ensure correct functioning of the pipeline
            . As these interfaces can be rather complex, it is necessary for the 
            workflow engine to provide an intuitive way for users to create 
            interfaces for their custom tools.

            Early neuroimaging workflow engines, such as SPM, are monolithic, 
            and therefore, do not provide a mechanism for users to incorporate
            their custom tools \tristan{Users can still integrate tools as Matlab functions
            doing system calls}. Workflow engines, such as AA, were thus 
            conceived to enable engines such as SPM to be more modular. AA 
            allows users to define their tasks through XML specification. AA's 
            XML tasklist is simply an ordered list of tasks which also includes
            details on analysis-specific parameters. Dependencies are
            inferred by the program through analysis of the module interfaces.
            Module interfaces consist of MATLAB user script and an XML 
            descriptor. The descriptor contains details on the input and output
            data stream types (e.g. epi, structural, dicom\_header) 
            and the desired domain (e.g. study, subject, session). During 
            execution, each task is given its own unique folder to operate on. 
            The engine will copy data to and extract data from this folder.

>>>>

        Workflows, also known as pipelines, describe the flow of data from one 
        activity to another and are typically represented by a graph. \tristan{Not necessarily a DAG, see Nipype for instance, it has loops.
        I don't think you want to enter in a taxonomy of languages though, just say 'graph'}. Workflow activities, also referred to as 
        workflow interfaces or stages, encapsulate a tool through the use of an
        interface\tristan{Mention 'interface' here as an intro to sub-sec 2}. 
        Tools can be represented in many forms, including: command-line tools, 
        custom scripts integrated directly into the workflow code, web 
        services and software libraries.\tristan{A script is a command-line tool. I think tools may also be web services (Taverna) or just 
        software libraries (Dask)}. A workflow activity with all its 
        dependencies is considered ready to be staged.

        For a workflow engine to be considered successful, it must be simple to 
        compose workflows using that framework. New researchers should be able 
        to acquire the skills to compose worfklows without
        investing a significant amount of time in understanding it. Reuse of
        existing tools is also common occurrence in neuroinformatics, and 
        workflow engines need to accomodate this by undertaking a modular 
        approach and being easily extensible. With the sharing of data also 
        comes the sharing of workflows. For labs to share their workflows with
        the community at large, these workflows must be easily understood by the
        community. This relates to the reproducibility of studies, as it is 
        more than likely that easily understood workflows are reproducible. 
        \tristan{Perhaps mention that this also relates to the sharing
        of reproducible results -- VH: not sure if this is what you meant}.

        In this Chapter, we will compare and contrast the workflow composition 
        of seven neuroimaging frameworks (SPM, LONI, Nipype, PSOM, FastR, AA and
        Pydpiper), seven scientific workflow engines stemming from other fields
        (Taverna, Pegasus, Make, OpenMOLE, Nextflow, Galaxy, Toil), and three
        BigData frameworks (MapReduce, Spark, Dask). We will use two axes to
        evaluate workflow composition. Section~\ref{lang} will compare the 
        framework on the basis of programming language used. Section~\ref{ds}
        will then examine the differences in data structures between scientific
        and BigData frameworks. 
        Section~\ref{mod} will look at how easy it is to integrate existing 
        tools into the workflows.

        \section{Workflow language}\label{lang}
            The choice of workflow language (e.g. GUI, scripting language,
            programming language) greatly
            affects how easily it will get picked up by the community. Complex
            languages may mean greater efficiency of engines
            , but also result in extensive time spent on learning and developing
            the pipelines. Moreover, some researchers may not be well-versed in
            programming and may require very easy-to-use engines.

            To address this issue, some workflow engines have taken the role
            of employing a graphical user interface (GUI). This makes workflow 
            composition accessible to all researchers, including those with
            little to no programming background. The caveat to employing a 
            workflow engine with a GUI interface for workflow composition is
            that users are greatly limited by the tasks they can perform. For 
            instance, workflows that perform any form of iterative operations
            (e.g. machine-learning workflows) or workflows with conditionals
            (e.g. given a certain input, do not execute this activity) cannot
            be represented by a GUI. 
            Workflow engines that employ a worfklow composition GUI include:
            SPM, Taverna, OpenMOLE, LONI and Galaxy.
            \tristan{My conclusion on GUIs is that they are suitable only
            for very simple pipelines. Perhaps the intro could give an idea
            of the types of pipelines encountered, showing a simple one and
            a more complex one. No way fmriprep is described in a GUI.}

            As more experienced programmers may feel limited by a GUI, workflow
            engines have decided to provide users with the ability to describe
            their workflows in more flexible formats. Even those with GUIs for 
            workflow composition, such as LONI and OpenMOLE, allow more 
            experienced users to script their workflow. Four different 
            languages are used for describing scientific workflows: 1) Python, 
            2) MATLAB and GNU/Octave \tristan{I think the official name is GNU/Octave}, 3) Shell Scripting languages \tristan{scripting languages}, 4) Domain Specific Language (DSL). \tristan{I don't see why CWL and XML don't qualify as DSL} Workflows engines that 
            employ usage of Python include: Nipype, FastR, Pydpiper, Pegasus, Toil,
            MapReduce, Dask and Spark. \tristan{Dask? Spark?}.
            Python is an excellent choice as a programming language for 
            scientific workflows, particularly neuroinformatics, due to its 
            widespread use within the community. Other advantages of 
            programming in Python include: a wide array of available libraries,
            particularly neuroimaging-specific ones such as Nilearn~\cite{nilearn} and Nibabel~\cite{matthew_brett_2018_1287921}
            and more general, but heavily used in neuroimaging, libraries such
            as SciPy~\cite{scipy} and Scikit Learn~\cite{pedregosa2011scikit} \tristan{mention scipy, sci-kit learn, etc}
            , and an lower learning curve compared to other 
            programming languages. Additionally, Python is platform independent
            meaning it can be installed on any system. In terms of BigData 
            frameworks that employ Python, Dask is exclusively written in Python
            , whereas Hadoop MapReduce and Spark both have interfaces to Python
            while being written in Java and Scala, respectively.

            Another widely-used high-level programming language in the 
            neuroinformatics community is MATLAB/Octave. Workflow engines which
            use this language include: PSOM, SPM, and Automatic analysis. Like 
            Python, MATLAB and GNU/Octave are platform-independent and also easy to use. In addition, MATLAB has 
            been found to exhibit better performance compared to Python for 
            common technical tasks. It also provides an integrated environment
            for programming. A 
            downfall to imposing MATLAB as programming language is that it is proprietary, thus imposing a fee on 
            anyone wishes to program in that language or have access to their diverse array of libraries \tristan{You should also mention the
            advantage of Matlab: easy to learn, integrated ecosystem, 
            performance, see 
            \url{https://www.mathworks.com/products/matlab/matlab-vs-python.html}}. 
            To offset this, PSOM ensure compatibility with the GNU 
            Octave programming language, thus 
            removing the requirement to purchase software for workflow 
            composition.

            \tristan{This paragraph should start with ``Shell scripting ...". The structuration of this section by language
            is great, but the writing of this paragram doesn't put it forward.}
            Many researchers have been exposed to Shell scripting languages as 
            several scientific workflows are composed in UNIX-based 
            environments. These environments typically have Make installed by
            default eliminating the need for users to install it manually.
            These features make workflow engine Make desirable for scientific
            computing.
            As Make is exclusive to UNIX environments, it is not 
            platform-independent. However, Make has the flexibility of being
            easily extensible and can interface directly with any command-line
            tool. Shell scripting, nevertheless, is generally not as intuitive
            as programming languages like Python and MATLAB.

            Domain Specific Languages (DSL) are also used to compose workflows.
            The can be made up of any language (e.g. XML, CWL, Scala and Groovy) that has been adapted for use in 
            a specific domain.
            XML is the language of choice in  
            workflow engines such as Pegasus and LONI. Using a markup language
            such as XML have the advantage of having access to 
            language-independent parsers and validators. However, the use of a 
            markup language removes some of the flexibility. \tristan{Before you explain the downside, 
            you should say what are the advantages: mainly language-independent parsers and validation.} Users wanting to 
            include 
            custom scripts as workflow activities must do so by creating a 
            command-line interface for their custom script. Pegasus, however,
            does provide many interfaces to describe the pipeline in including
            Java, Python and Perl.

            Another example of a DSL is a Common Workflow
            Language (CWL). CWL can be seen in workflow engines like Toil. 
            It is similar to XML in that its main difference is that it is 
            YAML/JSON-based.
            \tristan{It is a YAML-based DSL for workflows. Just like Pegasus' DAX is an XML-based DSL}. Files can either be written in JSON or YAML formats. CWL is 
            based on workflow engines like Make \tristan{? I don't think CWL relies on make, does it?}, but differs in that tasks
            are isolated \tristan{inputs and outputs are somewhat explicit in a Makefile}. Similarly to 
            make, CWL is only available on Linux and OSX platforms \tristan{strange, the CWL interpreter is in Python so I'd expect it to run anywhere}. \note{cite cwl 
            website}

            Programming language-based DSL workflow engines include OpenMOLE, which is  
            derived from Scala, and Nextflow \tristan{Nextflow?}, which is derived from the Apache 
            Groovy programming language. While both are written on top of the 
            Java platform, Nextflow is only compatible with Linux and OSX \tristan{How about using Linux everywhere instead of UNIX-based?} 
            environments. These programming languages are not otherwise commonly
            used in neuroimaging, meaning that users must learn specific 
            languages that would not otherwise be used in their field.

@@

            Since MapReduce, Spark and Dask all provide interfaces to Python,  
            they are good candidates for neuroimaging workflow engines. In addition
            Spark also interfaces with R, another programming language commonly
            used in neuroimaging.

            \section{Data structures}

                The data structures made available by workflow engines dictate
                the maximum performance available to a workflow. Scientific
                workflows are generally file-based, meaning that data, in the 
                form of files, will be 
                transferred across the network and I/O must be
                performed at each workflow activity. It is possible for some 
                data to remain in memory with scientific workflows, but these 
                are typically basic types such as numbers, strings and lists.
                More complex types, however, can be seen in workflow engines 
                such as PSOM which accept nested structures as long as the
                structures's terminal fields are either strings or cells of 
                strings. Due to workflow engines being file-based, performance
                is limited, particularly with BigData.

                In order to improve performance, BigData frameworks introduced
                data-centric data structures. MapReduce is key-value based, 
                therefore, data with the same keys would be located at the
                same nodes. As MapReduce still requires file-based I/O, the 
                amount of I/O remains similar to that of scientific workflows. 
                However, the key-value structures help to reduce the amount 
                of data transfers by promoting data-locality.

                The MapReduce key-value pair data structure is an effective 
                data structure for describing workflows, but is limited to only
                batch workflows and can be improved in terms of performance. 
                The resilient distributed datasets 
                (RDD)~\cite{Zaharia:2012:RDD:2228298.2228301}, Spark's main
                abstractions addresses these 
                issues by being a shared-memory structure. They 
                are immutable and only permit coarse-grained edits to ensure 
                fault-tolerance. The RDDs shared memory enables a reduction in
                I/O operation as data can be maintained in memory. Spark will only read 
                and write data to and from disk when data exceeds available 
                memory or when data needs to be shuffled around, as is the case
                with all Spark actions and certain transformations such as 
                \textit{join} and \textit{reduceByKey}. Moreover, RDDs permit
                workflows to be evaluated lazily. By being able to look at the
                entire workflow before evaluation, Spark can select the most
                performant methods for evaluating the data. 
                The RDD additionally expands its use to additional applications
                by enabling the expression of both iterative and interactive
                workflows. Furthermore, Spark provides an additional data 
                structure to enable the efficient processing of tabular data.
                This data structure is know as the 
                DataFrame~\cite{Armbrust:2015:SSR:2723372.2742797}.

                Dask builds off of Spark by not only providing data 
                structures similar to Spark's RDDs and Dataframes, Dask Bag and 
                DataFrame, but by also providing an abstraction for 
                larger-than-memory matrices, the Dask array. Furthermore, it is
                possible to use common Python APIs (e.g. NumPy\note{cite} and 
                Pandas DataFrame~\cite{mckinney2011pandas}) to process the 
                data. Although Spark does not have a datastructure for large 
                matrices, it has an RDD-based API, known as \textit{linealg}
                for similar processing of large 
                matrices~\cite{BosaghZadeh:2016:MCO:2939672.2939675}.

            \tristan{So this is now about data structures, not just language.
            This is really excellent, but this should perhaps go into a 
            specific sub-section. I think you could mention that 
            scientific workflow engines traditionally rely on files 
            only, and simple types, but that big data engines have 
            invested a lot in data structures, starting from key-value 
            pair representations in MR to RDD and Dask arrays. Spark is 
            actually built around RDDs, this is salient-enough to be 
            discussed a bit more. It actually makes a lot of sense that 
            data-focused engines are built around data structures 
            instead of control constructs. The ACM Com Spark paper makes it clear
            that unifying data structures is key to performance and interoperability, 
            because it allows data to remain in-memory instead of having to go back
            and forth to different environments. I would only mention linealg 
            in the description of Dask arrays. So, how about a 
            sub-section 'data structures' with 4 paragraphs: (1) 
            scientific and neuroimaging engines, (2) Big-Data, MR, (3) 
            Spark's RDDs and DataFrames, (4) Dask arrays, mentioning 
            linealg. }

        \section{Tool interfaces}\label{mod}
            \tristan{Since this section is about interfaces, I would
            rather call it ``Interfaces" or ``Tool interfaces".}
            Often times, users will want to integrate existing tools into their 
            workflows. In order for workflows to communicate effectively with
            the tools, it is required that an interface be created. Workflow 
            interfaces may range from simple command-line calls, to more 
            complex ones that track inputs, outputs and other parameters. 
            Furthermore, they ensure
            that all necessary parameters are correctly defined and in the 
            correct order,  capture all of the 
            standard input/output and create folders to encapsulate task inputs
            and outputs. Workflow engines typically rely on more complex types 
            of interfaces in order to ensure correct functioning of the pipeline
            . As these interfaces can be rather complex, it is necessary for the 
            workflow engine to provide an intuitive way for users to create 
            interfaces for their custom tools. Workflow interface can be 
            divided into two groups: those that are described using a 
            programming language and those that are described using DSL.

            Workflow engines that utilize programming languages include: SPM,
            One of the earliest neuroimaging workflow engines, 
            Early neuroimaging workflow engines, such as SPM, are monolithic, 
            and therefore, do not provide a default interface by which users 
            can integrate their tools\tristan{Users can still integrate tools as Matlab functions
            doing system calls}. Workflow engines, such as AA, were 
            created to enable engines such as SPM to be more modular. AA 
            allows users to define their tasks through XML specification. AA's 
            XML tasklist is simply an ordered list of tasks which also includes
            details on analysis-specific parameters. Dependencies are
            inferred by the program through analysis of the module interfaces.
            Module interfaces consist of MATLAB user script and an XML 
            descriptor. The descriptor contains details on the input and output
            data stream types (e.g. epi, structural, dicom\_header) 
            and the desired domain (e.g. study, subject, session). During 
            execution, each task is given its own unique folder to operate on. 
            The engine will copy data to and extract data from this folder.
